Web Page Visualization Code

### 2024-08-25 Scripts - Data Cleaning and Visuals/_CSV Cleaning.Rmd
changed directory locations and such
fixed directories in code

## Reset
```{r}
rm(list = ls()) 
setwd("/Users/emerson/Github/usenet_early_histories_project")
```

@@

# Load Directories
threads_directory <- "CSV Files/Threads"
comments_directory <- "CSV Files/Comments"

# Load the datasets
all_threads <- read.csv("CSV Files/Threads/combined_threads.csv")
all_comments <- read.csv("CSV Files/Comments/combined_comments.csv")

>>>>

## Reset
```{r}
rm(list = ls()) 
setwd("/Users/emerson/Github/usenet_AIDs_discourses_webpage")
```

@@

# Load Directories
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "combined_threads.csv"))
all_comments <- read.csv(file.path(comments_directory, "combined_comments.csv"))

### 2024-08-25 Scripts - Data Cleaning and Visuals/_Webpage Visualizations Code.Rmd
fixed directories in code

```{r R Read and Clean CSVs}
# Load Directories
threads_directory <- "CSV Files/Threads"
comments_directory <- "CSV Files/Comments"

# Load the datasets
all_threads <- read.csv("CSV Files/Threads/combined_threads_cleaned.csv")
all_comments <- read.csv("CSV Files/Comments/combined_comments_cleaned.csv")

@@

```{python Import necessary Python libraries}
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy
```

```{python Python Read CSVs}
all_comments = pd.read_csv("CSV Files/Comments/comments_cleaned_82TO89.csv")
all_threads = pd.read_csv("CSV Files/Threads/threads_cleaned_82TO89.csv")
```

# Initial Visualizations
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/distribution_of_comments_per_newsgroup.png')
plt.show()
```

@@

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Across All Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig('images and tables/number_of_threads_over_time.png')
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.barplot(data=avg_comments_per_thread, x='newsgroup', y='Number.of.Messages', order=avg_comments_per_thread.sort_values('Number.of.Messages', ascending=False)['newsgroup'])
plt.title('Average Number of Comments per Thread by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Average Number of Comments')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/average_comments_per_thread_by_newsgroup.png')
plt.show()
```

```{python Sentiment Score Distribution Across All Comments}
plt.figure(figsize=(10, 6))
sns.histplot(all_comments['SentimentScore'], bins=30, kde=True)
plt.title('Sentiment Score Distribution Across All Comments')
plt.xlabel('Sentiment Score')
plt.ylabel('Frequency')
plt.tight_layout()
plt.savefig('images and tables/sentiment_score_distribution_across_all_comments.png')
plt.show()
```

@@

# Save the figure
plt.savefig('images and tables/top_25_most_active_users_by_newsgroup.png')
plt.show()
```

@@

# Create the heatmap
plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='viridis')
plt.title('Daily Activity Heatmap Across All Newsgroups')
plt.xlabel('Day of Week')
plt.ylabel('Hour of Day')
plt.tight_layout()
plt.savefig('images and tables/combined_daily_activity_heatmap.png')
plt.show()
```

```{python Word Clouds!}
import pandas as pd
from wordcloud import WordCloud
import matplotlib.pyplot as plt
from nltk.corpus import stopwords
import nltk

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_all, interpolation='bilinear')
plt.axis('off')
plt.title('Most Common Words in All Usenet Comments')
plt.tight_layout()
plt.savefig('images and tables/word_cloud_all_comments.png')
plt.show()

@@

    plt.figure(figsize=(10, 6))
    plt.imshow(wordcloud_group, interpolation='bilinear')
    plt.axis('off')
    plt.title(f'Most Common Words in {newsgroup}')
    plt.tight_layout()
    plt.savefig(f'images and tables/word_cloud_{newsgroup}.png')
    plt.show()
```

@@

# Calculate cumulative count of newsgroups created over time
plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).newsgroup.nunique().cumsum().plot(kind='line')
plt.title('Growth of Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Cumulative Number of Newsgroups')
plt.tight_layout()
plt.savefig('images and tables/growth_of_newsgroups_over_time.png')
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.scatterplot(data=author_stats, x='Threads_Initiated', y='Comments_Made', alpha=0.6)
plt.title('Author Engagement: Comments Made vs. Threads Initiated')
plt.xlabel('Number of Threads Initiated')
plt.ylabel('Number of Comments Made')
plt.tight_layout()
plt.savefig('images and tables/author_engagement_scatterplot.png')
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(sentiment_over_time['Date'], sentiment_over_time['SentimentScore'], marker='o', linestyle='-')
plt.title('Average Sentiment Over Time Across All Newsgroups')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_over_time.png')
plt.show()
```

@@

plt.figure(figsize=(12, 6))
sns.boxplot(x='newsgroup', y='SentimentScore', data=all_comments)
plt.title('Sentiment Distribution by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_distribution_by_newsgroup.png')
plt.show()
```

@@

plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='coolwarm', center=0)
plt.title('Monthly Sentiment Heatmap by Newsgroup')
plt.xlabel('Month')
plt.ylabel('Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/monthly_sentiment_heatmap.png')
plt.show()
```

@@

plt.figure(figsize=(14, 8))
sns.lineplot(data=sentiment_by_newsgroup, x='Date', y='SentimentScore', hue='newsgroup', marker='o')
plt.title('Average Sentiment Over Time by Newsgroup')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_over_time_by_newsgroup.png')
plt.show()
```

@@

plt.figure(figsize=(8, 6))
sns.countplot(data=all_comments, x='SentimentPolarity', palette=['red', 'green'])
plt.title('Sentiment Polarity Distribution')
plt.xlabel('Sentiment Polarity')
plt.ylabel('Number of Comments')
plt.tight_layout()
plt.savefig('images and tables/sentiment_polarity_distribution.png')
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(all_comments['Date'], all_comments['RollingSentiment'], color='purple')
plt.title('Sentiment Trend Analysis with Rolling Average')
plt.xlabel('Date')
plt.ylabel('Rolling Average Sentiment Score (30-day window)')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig('images and tables/sentiment_trend_rolling_average.png')
plt.show()
```

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
plt.savefig('images and tables/word_cloud_positive_sentiment.png')
plt.show()

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_negative, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Negative Sentiment Comments')
plt.tight_layout()
plt.savefig('images and tables/word_cloud_negative_sentiment.png')
plt.show()
```

@@

# Save the network graph to an HTML file with full width and height
visSave(network_graph, file = "Images and Tables/network_graph.html")

@@

# Inject the legend into the HTML file
html_file <- "Images and Tables/network_graph.html"
html_content <- readLines(html_file)
html_content <- c(html_content, html_legend)
writeLines(html_content, html_file)
```

>>>>

```{r R Define Directories and Read/Clean CSVs}
# Load Directories
output_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage"
threads_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads"
comments_directory <- "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments"

# Load the datasets
all_threads <- read.csv(file.path(threads_directory, "combined_threads_cleaned.csv"))
all_comments <- read.csv(file.path(comments_directory, "combined_comments_cleaned.csv"))

@@

```{python Import necessary Python libraries}
import os
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy
```

```{python Python Define Directories and Read CSVs}
# Define directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"

# Load the datasets with the correct file paths
all_threads = pd.read_csv(os.path.join(threads_directory, "threads_cleaned_82TO89.csv"))
all_comments = pd.read_csv(os.path.join(comments_directory, "comments_cleaned_82TO89.csv"))
```

# Initial Visualizations
```{python Distribution of Comments per Newsgroup}
plt.figure(figsize=(10, 6))
sns.countplot(data=all_comments, x='newsgroup', order=all_comments['newsgroup'].value_counts().index)
plt.title('Distribution of Comments per Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/distribution_of_comments_per_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Across All Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/number_of_threads_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.barplot(data=avg_comments_per_thread, x='newsgroup', y='Number.of.Messages', order=avg_comments_per_thread.sort_values('Number.of.Messages', ascending=False)['newsgroup'])
plt.title('Average Number of Comments per Thread by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Average Number of Comments')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/average_comments_per_thread_by_newsgroup.png"))
plt.show()
```

```{python Sentiment Score Distribution Across All Comments}
plt.figure(figsize=(10, 6))
sns.histplot(all_comments['SentimentScore'], bins=30, kde=True)
plt.title('Sentiment Score Distribution Across All Comments')
plt.xlabel('Sentiment Score')
plt.ylabel('Frequency')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_score_distribution_across_all_comments.png"))
plt.show()
```

@@

# Save the figure
plt.savefig(os.path.join(output_directory, "images and tables/top_25_most_active_users_by_newsgroup.png"))
plt.show()
```

@@

# Create the heatmap
plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='viridis')
plt.title('Daily Activity Heatmap Across All Newsgroups')
plt.xlabel('Day of Week')
plt.ylabel('Hour of Day')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/combined_daily_activity_heatmap.png"))
plt.show()
```

```{python Word Clouds!}
import pandas as pd
from wordcloud import WordCloud
import matplotlib.pyplot as plt
from nltk.corpus import stopwords
import nltk
import os

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_all, interpolation='bilinear')
plt.axis('off')
plt.title('Most Common Words in All Usenet Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_all_comments.png"))
plt.show()

@@

    plt.figure(figsize=(10, 6))
    plt.imshow(wordcloud_group, interpolation='bilinear')
    plt.axis('off')
    plt.title(f'Most common words in {newsgroup}')
    plt.tight_layout()

    # Use f-string to save the file with the specific newsgroup name
    plt.savefig(os.path.join(output_directory, f"images and tables/word_cloud_{newsgroup}.png"))
    plt.show()
```

@@

# Calculate cumulative count of newsgroups created over time
plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).newsgroup.nunique().cumsum().plot(kind='line')
plt.title('Growth of Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Cumulative Number of Newsgroups')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/growth_of_newsgroups_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
sns.scatterplot(data=author_stats, x='Threads_Initiated', y='Comments_Made', alpha=0.6)
plt.title('Author Engagement: Comments Made vs. Threads Initiated')
plt.xlabel('Number of Threads Initiated')
plt.ylabel('Number of Comments Made')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/author_engagement_scatterplot.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(sentiment_over_time['Date'], sentiment_over_time['SentimentScore'], marker='o', linestyle='-')
plt.title('Average Sentiment Over Time Across All Newsgroups')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
sns.boxplot(x='newsgroup', y='SentimentScore', data=all_comments)
plt.title('Sentiment Distribution by Newsgroup')
plt.xlabel('Newsgroup')
plt.ylabel('Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_distribution_by_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 8))
sns.heatmap(heatmap_data, cmap='coolwarm', center=0)
plt.title('Monthly Sentiment Heatmap by Newsgroup')
plt.xlabel('Month')
plt.ylabel('Newsgroup')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/monthly_sentiment_heatmap.png"))
plt.show()
```

@@

plt.figure(figsize=(14, 8))
sns.lineplot(data=sentiment_by_newsgroup, x='Date', y='SentimentScore', hue='newsgroup', marker='o')
plt.title('Average Sentiment Over Time by Newsgroup')
plt.xlabel('Date')
plt.ylabel('Average Sentiment Score')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_over_time_by_newsgroup.png"))
plt.show()
```

@@

plt.figure(figsize=(8, 6))
sns.countplot(data=all_comments, x='SentimentPolarity', palette=['red', 'green'])
plt.title('Sentiment Polarity Distribution')
plt.xlabel('Sentiment Polarity')
plt.ylabel('Number of Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_polarity_distribution.png"))
plt.show()
```

@@

plt.figure(figsize=(12, 6))
plt.plot(all_comments['Date'], all_comments['RollingSentiment'], color='purple')
plt.title('Sentiment Trend Analysis with Rolling Average')
plt.xlabel('Date')
plt.ylabel('Rolling Average Sentiment Score (30-day window)')
plt.xticks(rotation=45)
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/sentiment_trend_rolling_average.png"))
plt.show()
```

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_positive, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Positive Sentiment Comments')
plt.tight_layout()
0_output_path = os.path.join(output_directory, "images and tables/word_cloud_positive_sentiment.png"))
plt.savefig(0_output_path)
plt.show()

@@

plt.figure(figsize=(10, 6))
plt.imshow(wordcloud_negative, interpolation='bilinear')
plt.axis('off')
plt.title('Top Words in Negative Sentiment Comments')
plt.tight_layout()
plt.savefig(os.path.join(output_directory, "images and tables/word_cloud_negative_sentiment.png"))
plt.show()
```

@@

# Save the network graph to an HTML file with full width and height
network_graph_path <- file.path(output_directory, "images and tables/network_graph.html")
visSave(network_graph, file = network_graph_path)

@@

# Inject the legend into the HTML file
html_content <- readLines(network_graph_path)
html_content <- c(html_content, html_legend)
writeLines(html_content, network_graph_path)
```
